### 2013-08-28 pystruct/paper.tex
more on algorithms for structured learning, but broke the algorithm listings?

Structured prediction can be defined as making a prediction $f(x)$ by maximizing a
compatibility function $g$ between an input $x$ and possible labels
$y$~\citep{nowozin2011structured}:
\begin{equation}
    f(x) = \argmax_{y in \mathcal{Y}} g(x, y)
\end{equation}
While using arbitrary functions is possible, and was expored
in some recent works % TODO cite dtf, conditional neural fields
most current approaches use linear functions, leading to:
\begin{equation}\eqlabel{main_equation}
    f(x) = \argmax_{y \in \mathcal{Y}}\  \theta^T \Phi(x, y).
\end{equation}
Here, $y$ is a \emph{structured} label, $\Phi$ is a joint feature function of
$x$ and $y$, and $\theta$ are parameters of the model. \emph{Structured} means
that $y$ is more complicated than a single output class, for example a label
for each word in a sentence or a label for each pixel in an image.
Learning structured prediction means learning the parameters $\theta$ from training data.
The particular model that is used is completely encoded in $\Phi(x, y)$, which manifests
the relation between input $x$ and output $y$. As $\mathcal{Y}$ is typically very large,
it is crucial to exploit the particular form of $\Phi(x, y)$ to solve the maximization problem
in \Eqref{main_equation}.

While $y$ could be a complicated like a parsing tree or the geometric configuration of a molecule,
many setting, such as the image segmentation setting we are interested, can be reduced to the case
where $y$ is a vector of discrete labels $\mathcal{Y} = \{0, \dotsc, k\}^n$. %TODO n varies.
In the following, we will only discuss this multivatiate case. In general, $n$ is often different
for different inputs $x$, such as image with different number of (super) pixels.
We will ignore this in our notation to simplify the presentation.

\subsection{Factor Graphs and the Relation to Graphical Models}
In the case when $y$ is multivariate, a very general and widely used method to
specify the structure of a model, and therefore $\Phi$, is using \emph{factor
graphs}. A factor graph is a bipartite graph $(\mathcal{V}, \mathcal{F},
\mathcal{E})$, consisting of variable nodes $\mathcal{V}$, factor nodes
$\mathcal{F}$ and edges $\mathcal{E}$ connecting variables to factors. The
\emph{scope} $N_F$ of a factor $F \in \mathcal{F}$ is defined as
\begin{equation}
    N_F = \{ v \in \mathcal{V} \,|\, (v,F) \in \mathcal{E} \}
\end{equation}
The variable nodes of the factor graph correspond to the entries of the variables $y$,
that is $\mathcal{V} = \{0, \dotsc, n\}$, and each factor node is associated with a \emph{factor} or \emph{potential function}
$\psi_F$.
A factor graph represents a function\footnote{Traditionally factor graphs represent \emph{products} of factors.
To simplify presentation, we work directly in the log-domain of the product representation.}
\begin{equation}\eqlabel{log_factor_graph}
    g(x, y) = \sum_{F \in \mathcal{F}} \psi_F(x, y_{N_F})
\end{equation}
Here, $y_{N_F}$ denotes the entries of $y$ indexed by $N_F$.

The benefit of using the factor graph representation is that it decomposes the
function over the variables of interest $y_i$ and makes. This allows us to
apply efficient optimization procedures for the maximization in
\Eqref{mainequation} by exploiting the graph structure of the factor graph.

To obtain a linear function as in \Eqref{mainequation} from
\Eqref{log_factor_graph}, we can simply let each $\psi$ be of the form
\begin{equation}\eqlabel{general_psi}
    \psi_F(x, y_{N_F}) = \theta_F^T \Phi_F(x, y_{N_F}).
\end{equation}
The by far most common form is 
\begin{equation}\eqlabel{linear_psi}
    \psi_F(x, y_{N_F}) = \theta_{F, y_{N_F}}^T \phi_F(x),
\end{equation}
where $\phi_F(x)$ is a vector representation of the input $x$, and there are
different parameter vectors $\theta_{F, y_{N_F}}$ for each possible assignment
of $y_{N_F}$.

Both, \Eqref{general_psi} and \Eqref{linear_psi} are instantiations of the general
linear form \Eqref{main_equation}. To see this, for \Eqref{general_psi} we simply
concatenate the individual components for all $f \in \mathcal{F}$:
\begin{align}
    \theta &= \bigoplus_{F \in \mathcal{F}} \theta_F\\
    \Phi(x, y) &= \bigoplus_{F \in \mathcal{F}} \Phi_F(x, y)
\end{align}
%TODO linear psi explicitly

The benefit of using the factor graph representation is that it allows us to
apply efficient optimization procedures for the maximization in
\Eqref{mainequation} by exploiting the graph structure of the factor graph.

@@

During learning, the presence of the factor $Z$ in \Eqref{graphicalmodel}
introduces additional complications. As we only address the problem of making
predictions, not modeling probabilities, there are no clear benefits from the
probabilistic approach.  Consequently, we will work with the more direct
structured prediction approach of \Eqref{mainequation} and
\Eqref{log_factor_graph} instead.

% TODO relate to computer vision here ??? Pairwise models?

\subsection{The Maximum Margin Approach to Structured Learning}
% margin BLABLA here?
For a given loss $\Delta$, the parameters $\theta$ are learned by minimizing
the loss base soft-margin objective
\begin{equation}\label{mainequation}
    \min_\theta \frac{1}{2} ||\theta||^2 + C \sum_i  r_i(\theta)
\end{equation}
with regularization parameter $C$, where $r_i$ is an hinge-loss like upper
bound on $\Delta$ empirical risk:
\[r_i(x_i, y_i, y) = [\max_{y \in \mathcal{Y}} \Delta(y_i, y) + \left<\theta, \phi(x_i, y) - \phi(x_i, y_i) \right >]_+ \]
\citep{ratliff2007online} derive convergence rates for a stochastic version of the subgradient of  Equation~\ref{mainequation}:
\begin{equation}\label{subgradient}
    g := \phi(x_i, y) - \phi(x_i, y_i) + \theta / C
\end{equation}
leading to a simple iterative optimization.

\section{Learning Algorithms for Linear Max-Margin Structured Prediction}
% TODO algorithms here
\subsection{The Cutting Plane Method}\label{cutting_plane}

For a given loss $\Delta$, the parameters $\theta$ are learned by minimizing
the loss-based soft-margin objective
\begin{equation}\label{eq:mainequation}
\min_\theta \frac{1}{2} ||\theta||^2 + C \sum_i  r_i(\theta)
\end{equation}
with regularization parameter $C$, where $r_i$ is a hinge-loss-like upper
bound on the empirical $\Delta$-risk:
\[r_i(x^i, y^i, y) = \left [\max_{y \in \mathcal{Y}} \Delta(y^i, y) + \left<\theta, \phi(x^i, y) - \phi(x^i, y^i) \right > \right]_+ \]

We solve the following reformulation of Equation~\Eqref{mainequation}, known as one-slack QP formulation:
\begin{align}\label{eq:oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\phi(x^i, y^i) - \phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
using the cutting plane method described in
Algorithm~\ref{alg_cutting_plane}~\citep{joachims2009cutting}.

The cutting plane method alternates between solving Equation~\Eqref{oneslack}
with a working set $\W$ of constraints, and expanding the working set using the
current $\theta$ by finding $\mathbf{y}$ corresponding to the most violated constraint,
using a separation oracle $I$.
We investigate the construction of $\W$ and the influence of $I$
on learning.

%TODO unstructured!!

Intuitively, the one-slack formulation corresponds to joining all training
samples into a single training example $(\mathbf{x}, \mathbf{y})$ that has no
interactions between variables corresponding to different data points.
Consequently, only a single constraint is added in each iteration of
Algorithm~\ref{alg_cutting_plane}, leading to very small $\W$. We further use
pruning of unused constraints, as suggested by \citet{joachims2009cutting},
resulting in the size of $\W$ being in the order of hundreds for all experiments.

We also use another enhancement of the cutting plane algorithm introduced by
\citet{joachims2009cutting}, the caching oracle. For each training example $(x^i, y^i)$,
we maintain a set $C^i$ of the last $r$ results of loss-augmented inference
(line~\ref{get_cutting_plane} in Algorithm~\ref{alg_cutting_plane}).
For generating a new constraint $(\hat{y}^1, \dotsc, \hat{y}^n)$ we find
\[ 
    \hat{y}^i \leftarrow \argmax_{\hat{y}\in C^i} \sum_{i=1}^n \Delta(y^i, \hat{y}) - \theta^T \sum_{i=1}^n [\phi(x^i, y^i) - \phi(x^i, \hat{y})]
\]
by enumeration of $C^i$ and continue until line~\ref{convergence_check}.
Only if $\xi' - \xi < \epsilon$, that is the produced constraint is not violated, we
return to line~\ref{get_cutting_plane} and actually invoke the separation
oracle $I$.

@@

>>>>

Structured prediction can be defined as making a prediction $f(x)$ by maximizing a
compatibility function $g$ between an input $x$ and possible labels
$y$~\citep{nowozin2011structured}:
\begin{equation}
    f(x) = \argmax_{y \in \mathcal{Y}} g(x, y)
\end{equation}
The computation of $y$ in the above equation is often referred to as inference
or prediction.
While using arbitrary functions is possible, and was expored
in some recent works % TODO cite dtf, conditional neural fields
most current approaches use linear functions, leading to:
\begin{equation}\eqlabel{main_equation}
    f(x) = \argmax_{y \in \mathcal{Y}}\  \theta^T \Phi(x, y).
\end{equation}
Here, $y$ is a \emph{structured} label, $\Phi$ is a joint feature function of
$x$ and $y$, and $\theta$ are parameters of the model. \emph{Structured} means
that $y$ is more complicated than a single output class, for example a label
for each word in a sentence or a label for each pixel in an image.
Learning structured prediction means learning the parameters $\theta$ from training data.
The particular model that is used is completely encoded in $\Phi(x, y)$, which manifests
the relation between input $x$ and output $y$. As $\mathcal{Y}$ is typically very large,
it is crucial to exploit the particular form of $\Phi(x, y)$ to solve the inference problem
of \Eqref{main_equation}.

While $y$ could be a complicated like a parsing tree or the geometric
configuration of a molecule, many setting, such as the image segmentation
setting we are interested, can be reduced to the case where $y$ is a vector of
discrete labels $\mathcal{Y} = \{1, \dotsc, k\}^n$.
In the following, we will only discuss this multivatiate case. In general, $n$ is often different
for different inputs $x$, such as image with different number of (super) pixels.
We will ignore this in our notation to simplify the presentation.

\subsection{Factor Graphs and the Relation to Graphical Models}
% one factor graph per instance?
In the case when $y$ is multivariate, a very general and widely used method to
specify the structure of a model, and therefore $\Phi$, is using \emph{factor
graphs}. A factor graph is a bipartite graph $(\mathcal{V}, \mathcal{F},
\mathcal{E})$, consisting of variable nodes $\mathcal{V}$, factor nodes
$\mathcal{F}$ and edges $\mathcal{E}$ connecting variables to factors. The
\emph{scope} $N_F$ of a factor $F \in \mathcal{F}$ is defined as
\begin{equation}
    N_F = \{ v \in \mathcal{V} \,|\, (v,F) \in \mathcal{E} \}
\end{equation}
The variable nodes of the factor graph correspond to the entries of the
variables $y$, that is $\mathcal{V} = \{1, \dotsc, n\}$, and each factor node
is associated with a \emph{factor} or \emph{potential function} $\psi_F$.
A factor graph represents a function\footnote{Traditionally factor graphs
 represent \emph{products} of factors.  To simplify presentation, we work
directly in the log-domain of the product representation.}
\begin{equation}\eqlabel{log_factor_graph}
    g(x, y) = \sum_{F \in \mathcal{F}} \psi_F(x, y_{N_F})
\end{equation}
Here, $y_{N_F}$ denotes the entries of $y$ indexed by $N_F$.

The benefit of using the factor graph representation is that it decomposes the
function over the variables of interest $y_i$ and makes. This allows us to
apply efficient optimization procedures for the maximization in
\Eqref{main_equation} by exploiting the graph structure of the factor graph.

To obtain a linear function as in \Eqref{main_equation} from
\Eqref{log_factor_graph}, we can simply let each $\psi$ be of the form
\begin{equation}\eqlabel{general_psi}
    \psi_F(x, y_{N_F}) = \theta_F^T \Phi_F(x, y_{N_F}).
\end{equation}
The by far most common form is 
\begin{equation}\eqlabel{linear_psi}
    \psi_F(x, y_{N_F}) = \theta_{F, y_{N_F}}^T \phi_F(x),
\end{equation}
where $\phi_F(x)$ is a vector representation of the input $x$, and there are
different parameter vectors $\theta_{F, y_{N_F}}$ for each possible assignment
of $y_{N_F} \in \mathcal{Y}_{N_F}$.

Both, \Eqref{general_psi} and \Eqref{linear_psi} are instantiations of the general
linear form \Eqref{main_equation}. To see this, for \Eqref{general_psi} we simply
concatenate the individual components for all $f \in \mathcal{F}$:
\begin{align}
    \theta &= \bigoplus_{F \in \mathcal{F}} \theta_F\\
    \Phi(x, y) &= \bigoplus_{F \in \mathcal{F}} \Phi_F(x, y_{N_F})
\end{align}
Writing down $\Phi$ and $\theta$ for the form \Eqref{linear_psi} is a little less compact:
\begin{align}
    \theta &= \bigoplus_{F \in \mathcal{F}}\ \bigoplus_{y_{N_F} \in \mathcal{Y}_{N_F}} \theta_{F, y_{N_F}}\\
    \Phi(x, y) &= \bigoplus_{F \in \mathcal{F}} \left (\phi_F(x) \otimes e_{y_{N_F}} \right )
\end{align}
where $e_{y_{N_F}} \in \mathbb{R}^{|\mathcal{Y}_{N_F}|}$ is the indicator for a
given variable setting $y_{N_F}$.
In words, $\Phi_F$ is build simply by creating a vector of
$|\mathcal{Y}_{N_F}|$ times the size of $\phi_F$, which is zero everywhere,
except for the place corresponding to $y_{N_F}$. %TODO unclear!

The benefit of using the factor graph representation is that it allows us to
apply efficient optimization procedures for the maximization in
\Eqref{main_equation} by exploiting the graph structure of the factor graph.

@@

During learning, the presence of the factor $Z$ in \Eqref{graphicalmodel}
introduces additional complications. As we only address the problem of making
predictions, not modeling probabilities, there are no clear benefits from the
probabilistic approach.  Consequently, we will work with the more direct
structured prediction approach of \Eqref{main_equation} and
\Eqref{log_factor_graph} instead.

% TODO relate to computer vision here ??? Pairwise models?
% talk about inference?

\section{Learning Algorithms for Linear Max-Margin Structured Prediction}
Maximum Margin learning is now one of the most popular methods to learn
structural models in computervision and in other fields.
There are several reasons for the popularity of linear maximum margin approaches:
\begin{description}
    \item[Loss-sensitivity] In contrast to probabilistic approaches, maximum margin learning approaches can directly
        minimize a user-specified loss.
    \item[Feasibility] If the loss decomposes over the factor graph that
        specifies $g$, then learning is feasible as soon as the maximization
        over $y$ in \Eqref{main_equation} can be caried out.
    \item[Generalization] The maximum margin principle yields generalization
        bounds using the effective complexity~\citep{taskar2003max}.
    \item[Strong Convexity] The resulting optimization problem is strongly
        convex, leading to efficient optimization and unique solutions.
\end{description}

For learning, a dataset $(x^{(1)}, y^{(1)}),\dotsc,(x^{(k)}, y^{(k)})$, together with a loss
\begin{equation}
    \Delta \colon \mathcal{Y} \times \mathcal{Y} \rightarrow \mathbb{R}.
\end{equation}
The parameters $\theta$ are learned by minimizing the loss based soft-margin
objective
\begin{equation}\eqlabel{learning_equation}
    \min_\theta \frac{1}{2} ||\theta||^2 + C \sum_i  \ell(x^{(i)}, y^{(i)}, \theta)
\end{equation}
with regularization parameter $C$. Here $r_i$ is an hinge-loss like upper bound
on $\Delta$ empirical risk:
\begin{equation}\eqlabel{loss_augmentation}
    \ell(x^{(i)}, y^{(i)}, \theta)= [\max_{y \in \mathcal{Y}} \Delta(y^{(i)}, y) + \theta^T \phi(x^{(i)}, y) - \theta^T \phi(x^{(i)}, y^{(i)}]_+
\end{equation}

This is an instance of regularized empirical risk minimization, with a
piecewise linear, convex upper bound on the loss. 
Finding the $y$ that corresponds to a maximum in \Eqref{loss_augmentation} is
a central part of all maximum-margin based learning algorithms, and is referred to
as loss-augmented prediction. For complex models, such as the ones used for
image segmentation, this optimization often dominates the learning process in
terms of computational complexity.
Therefore, it is often desireable to find learning algorithms that converge with
as little optimizations of the loss-augmented prediction problem as possible.

There are several popular algorithms to solve \Eqref{learning_equation}. We
will briefly review three standard algorithms: the one-slack and n-slack
cutting plane algorithms, a stochastic primal subgradient algorithm, and
recently proposed stochastic dual coordinate descent method.

\subsection{Stochastic Subgradient Descent}\seclabel{subgradient}
Arguably the most straight-foward way to approach \Eqref{learning_equation} is using subgradient descent.
In light of the complexity of solving the loss-augmented prediction problem in \Eqref{loss_augmentation},
is is natural to work in a stochastic setting (see \citet{ratliff2007online}).
%\citep{ratliff2007online} derive convergence rates for a stochastic version of the subgradient of  Equation~\ref{mainequation}:
%\begin{equation}\label{subgradient}
    %g := \phi(x_i, y) - \phi(x_i, y_i) + \theta / C
%\end{equation}
%leading to a simple iterative optimization.

\subsection{The N-Slack Cutting Plane Method}\seclabel{n_slack}
The n-slack cutting plane method~\citep{tsochantaridis2006large} reformulates \Eqref{learning_equation}
into a quadratic objective with a combinatorial number of constraints:
\begin{align}\label{eq:oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \sum_{i=1}^k \xi_i\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\phi(x^i, y^i) - \phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
As is not feasible to deal with all constraints, only a working set $\W$ of active constraints
is maintained, using the cutting plane method. The algorithm starts with an empty working set,
and in each iteration adds the most violated constraint to $\W$. Then, the quadratic program is solved
again, with the new set of constraints.
The algorithm terminates when no constraint can be found that is more violated then $\epsilon$,
which guarantees a suboptimality of at most $\epsilon$.

The complete algorithm is described in Algorithm~\ref{alg_n_slack}.

%\begin{algorithm*}[t]
    %\caption{N-Slack Cutting Plane Training of Structural SVMs \label{alg_n_slack}}
    %%FIXME

    %\begin{algorithmic}[1]
        %\require training samples $\{ (x^{(1)}, y^{(1)}), \dots, (x^{(n)}, y^{(n)})\}$, regularization parameter $c$, stopping tolerance $\epsilon$.
        %\ensure parameters $\theta$, slack $\xi$
        %\state $\w \leftarrow \emptyset$
        %\repeat
        %\state $(\theta, \xi) \leftarrow \displaystyle \argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + c \xi$\label{restricted}\\
        %\begin{equation*}
            %\text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}^{(1)}, \dots, \hat{y}^{(n)}) \in \w:
            %\left \langle \theta, \sum_{i=1}^n [\psi(x^{(i)}, y^{(i)}) - \psi(x^i, \hat{y}^{(i)})] \right \rangle \geq \sum_{i=1}^n \delta(y^{(i)}, \hat{y}^{(i)})
                %- \xi
            %\end{equation*}
            %\for {i=1, \dots, n}
            %\state
            %$\hat{y}^{(i)} \leftarrow i(x^{(i)}, y^{(i)}, \theta) := \displaystyle \argmax_{\hat{y}\in\mathcal{y}} \sum_{i=1}^n \delta(y^{(i)}, \hat{y}) - \left \langle \theta, \sum_{i=1}^n [\psi(x^{(i)}, y^{(i)}) - \psi(x^{(i)}, \hat{y})] \right \rangle$ \label{get_cutting_plane}
            %\endfor
            %\state $\w \leftarrow \w \cup \{ (\hat{y}^{(1)}, \dots, \hat{y}^{(n)}) \} $
            %\state $ \displaystyle \xi' \leftarrow  \sum_{i=1}^n \delta(y^{(i)}, \hat{y}^{(i)}) - \left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^{(i)}, \hat{y}^{(i)})] \right \rangle$
            %\until $\xi' - \xi < \epsilon$ \label{convergence_check}
        %\end{algorithmic}
    %\end{algorithm*}

\subsection{The 1-Slack Cutting Plane Method}\seclabel{one_slack}

\begin{algorithm*}[t]
    \caption{1-Slack Cutting Plane Training of Structural SVMs \label{alg_one_slack}}
    \begin{algorithmic}[1]
        \require training samples $\{ (x^{(1)}, y^{(1)}), \dots, (x^{(n)}, y^{(n)})\}$, regularization parameter $c$, stopping tolerance $\epsilon$.
        \ensure parameters $\theta$, slack $\xi$
        \state $\w \leftarrow \emptyset$
        \repeat
            \state $(\theta, \xi) \leftarrow \displaystyle \argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + c \xi$\label{restricted}\\
            \begin{equation*}
                \text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}^{(1)}, \dots, \hat{y}^{(n)}) \in \w:
                \left \langle \theta, \sum_{i=1}^n [\psi(x^{(i)}, y^{(i)}) - \psi(x^i, \hat{y}^{(i)})] \right \rangle \geq \sum_{i=1}^n \delta(y^{(i)}, \hat{y}^{(i)})
                - \xi
            \end{equation*}
            \for {i=1, \dots, n}
                \state
                $\hat{y}^{(i)} \leftarrow i(x^{(i)}, y^{(i)}, \theta) := \displaystyle \argmax_{\hat{y}\in\mathcal{y}} \sum_{i=1}^n \delta(y^{(i)}, \hat{y}) - \left \langle \theta, \sum_{i=1}^n [\psi(x^{(i)}, y^{(i)}) - \psi(x^{(i)}, \hat{y})] \right \rangle$ \label{get_cutting_plane}
            \endfor
            \state $\w \leftarrow \w \cup \{ (\hat{y}^{(1)}, \dots, \hat{y}^{(n)}) \} $
            \state $ \displaystyle \xi' \leftarrow  \sum_{i=1}^n \delta(y^{(i)}, \hat{y}^{(i)}) - \left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^{(i)}, \hat{y}^{(i)})] \right \rangle$
        \until $\xi' - \xi < \epsilon$ \label{convergence_check}
    \end{algorithmic}
\end{algorithm*}

The one-slack cutting plane method~\citep{joachims2009cutting} solves the
following reformulation of Equation~\Eqref{learning_equation}:
\begin{align}\label{eq:oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\phi(x^i, y^i) - \phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
Informally, the one-slack formulation corresponds to joining all training
samples into a single training example $(\mathbf{x}, \mathbf{y})$ that has no
interactions between variables corresponding to different data points, and
then applying the n-slack algorithm.
The complete algorithm is described in Algorithm~\ref{alg_one_slack}.

By construction only a single constraint is added in each iteration of
Algorithm~\ref{alg_one_slack}, leading to very small working sets $\W$.
This has the advantage of making the solution of the QP faster, as it contains
less variables. The down-side of this is that the loss-augmented prediction
problem has to be solve much more often until convergence.
%TODO convergence rate

\citet{joachims2009cutting}, who introduced the method, proposed two enhancements
to make the algorithm more efficient:
\begin{description}
    \item[Constraint Pruning] Members of the working set $\W$ can become inactive during learning.
        If a constraint has been inactive for a number of itertions, it is removed from $\W$, leading
        to smaller problem sizes.
    \item[Inference Caching] In the one-slack algorithm, each constraint is
        created using a combination of loss-augmented prediction results.
        Therefore, each of these predictions can be part of multiple
        constraints during learning.
        To exploit this, we maintain a set $C^i$ of the last $r$ results of
        loss-augmented inference for each training example $(x^i, y^i)$
        (line~\ref{get_cutting_plane} in Algorithm~\ref{alg_one_slack}).
        For generating a new constraint $(\hat{y}^1, \dotsc, \hat{y}^n)$ we
        find
        \[ \hat{y}^i \leftarrow \argmax_{\hat{y}\in C^i} \sum_{i=1}^n
            \Delta(y^i, \hat{y}) - \theta^T \sum_{i=1}^n [\phi(x^i, y^i) -
                \phi(x^i, \hat{y})] \]
        by enumeration of $C^i$ and continue until
        line~\ref{convergence_check}.  Only if $\xi' - \xi < \epsilon$, that is
        the produced constraint is not violated, we return to
        line~\ref{get_cutting_plane} and actually invoke the loss augmented
        prediction $I$.
\end{description}

\subsection{Stochastic Dual Coordinate Descent}\seclabel{dual_coordinate_descent}

@@

\section{Comparing Learning Algorithms}
%TODO experiments!!
